\documentclass[]{article}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\begin{center}
    \Large{\textbf{Sean Wald}} \\
    \small{\href{mailto:seantwald@gmail.com}{seantwald@gmail.com} \textbar (760)-717-4265 \textbar \href{https://www.linkedin.com/in/seantowald/}{Linkedin}} \\
\end{center}
\hrule

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{flushleft}
    \begin{tabular}{@{}p{0.5\textwidth}@{}p{0.5\textwidth}@{}}
        Hiring Manager & \hfill\today\\
    \end{tabular}
    Roblox\\


\end{flushleft}

\section*{Dear Recruiter,}


% Mention:
% * Proficient in one or more programming languages such as C, Lua, Java, Go, Node.js, Ruby, Python, C++, or Swift.
% * Passionate about games, user-generated content, and social networking.
% * A problem solver who excels in ambiguous environments and quickly develops proficiency in coding standards.

I am writing to express my interest in the New Grad Software Engineer position at Roblox. As a recent graduate in Computer Science and Mathematics from the University of California, 
San Diego, I have developed a keen interest in software engineering, particularly in creating tools, platforms, and games for end users. I am excited about the opportunity to advance 
my coding skills and work on projects that have a positive impact on people. \\
\\
My experience in software engineering includes my time at the Naval Air Warfare Center Weapons Division, where I worked with a full-stack team to develop an internal employee networking website, 
and my time working for a simulation and modeling team to model classified projects for the government. Through these projects, I gained experience with Node.js, 
Vue.js, PostgreSQL, C, C++, and Python, as well as modern coding standards such as Agile frameworks, version control with Git, and implementing CI/CD pipelines for 
automated testing. Additionally, I have DevOps experience from my time as a Lead Technician at the ITS service desk, where I troubleshooted DNS and DHCP issues, 
maintained virtual computers, databases, and ranges, and managed IP logs via internal software. I am an industrious worker who loves to tackle difficult tasks to 
develop immersive experiences for customers.\\
\\
During my time at UCSD, I completed coursework in Python, Java, C/C++, ARM-32 Assembly, Linear Optimization, Abstract Algebra, Dynamic Programming, Theory of Computation, 
Graph Theory, and Linear Algebra. My strong foundation in mathematics allows me to break down complex coding problems into their mathematical components, enabling me to better 
understand and solve them. I am eager to leverage my knowledge of mathematics and my coding expertise in the Software Engineer role at Roblox.\\
\\
Thank you for taking the time to review my application. I hope you will find me a valuable addition to the
Design, Product, Data, QA, and DevOps teams. I can be reached any time at (760) 717-4265 or via email at
swald@ucsd.edu or seantwald@gmail.com.\\
\\
Sincerely,\\
Sean Wald

\end{document}  